Quantifying the importance of an inference model in Bayesian phylogenetics

### 2019-12-17 content.tex
Use new naming

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single,
    label = {lst:create_alignment_params}, 
    caption = {Create an alignment.}
  ]
alignment_params <- create_alignment_params(
  sim_true_alignment_fun = get_sim_true_alignment_with_std_site_model_fun(
    mutation_rate = 0.1,
    site_model = create_jc69_site_model()
  ),
  root_sequence = create_blocked_dna(length = 1000)
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language = R,
  floatplacement = ht,
  frame = single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters.
]
twinning_params <- create_twinning_params(
  sim_twin_tree_fun = get_sim_bd_twin_tree_fun(),
  sim_twin_alignment_fun = get_sim_twin_alignment_with_std_site_model_fun()
)
\end{lstlisting}

>>>>

\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single,
    label = {lst:create_alignment_params}, 
    caption = {Create an alignment.}
  ]
alignment_params <- create_alignment_params(
  sim_tral_fun = get_sim_tral_with_std_nsm_fun(
    mutation_rate = 0.1,
    site_model = create_jc69_site_model()
  ),
  root_sequence = create_blocked_dna(length = 1000)
)
\end{lstlisting}

@@

\begin{lstlisting}[
  language = R,
  floatplacement = ht,
  frame = single,
  label = {lst:create_twinning_params},
  caption = Create the default twinning parameters.
]
twinning_params <- create_twinning_params(
  sim_twin_tree_fun = get_sim_bd_twin_tree_fun(),
  sim_twal_fun = get_sim_twal_with_std_nsm_fun()
)
\end{lstlisting}
